---
title: "Youtube New"
author: "Lanzo Siega"
date: "03/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages Used
```{r}
install.packages(c("jsonlite","plyr", "dplyr", "ggplot2", "scales"))
library(jsonlite)
library(plyr)
library(dplyr)
library(ggplot2)
library(scales)
```

Setting Working Directory
```{r}
getwd()
setwd("D:/Practice/Portfolio/youtube-new")
```

Reading CAVideos.csv and CA_category_id.json files, then checking structure of both datasets
```{r}
ca <- read.csv("CAvideos.csv", stringsAsFactors = F)

caID <- fromJSON("CA_category_id.json", flatten = T)
items <- caID[["items"]]
attach(c(ca, items))
```

# Descriptive Analysis

```{r}
summary(ca)
str(ca)
dim(ca)
View(ca)
```

```{r}
summary(items)
str(items)
dim(items)
View(items)
```

#Exploratory Data Analysis

correlation_matrix
```{r}
panel.cor <- function(x, y, digits=2, prefix="", cex.cor) 
{
    usr <- par("usr"); on.exit(par(usr)) 
    par(usr = c(0, 1, 0, 1)) 
    r <- abs(cor(x, y)) 
    txt <- format(c(r, 0.123456789), digits=digits)[1] 
    txt <- paste(prefix, txt, sep="") 
    if(missing(cex.cor)) cex <- 0.8/strwidth(txt) 
 
    test <- cor.test(x,y) 
    # borrowed from printCoefmat
    Signif <- symnum(test$p.value, corr = FALSE, na = FALSE, 
                  cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                  symbols = c("***", "**", "*", ".", " ")) 
 
    text(0.5, 0.5, txt, cex = cex * r) 
    text(.8, .8, Signif, cex=cex, col=2) 
}
numer <- ca[c("views", "likes", "dislikes", "comment_count")]
pairs(numer, lower.panel = panel.smooth, upper.panel = panel.cor)

calm <- lm(views~likes+dislikes+comment_count)
summary(calm)
```

Comment_count yields the highest correlation coefficient with each numerical variable.
```{r}
co <- head(ca$title[order(ca$comment_count, decreasing = T)], n = 10)
co
ca$title[ca$comment_count == max(ca$comment_count)]
```

Top Video by comment count
```{r}
co <- aggregate(comment_count~title,ca, FUN = sum)
top_co <- head(co[order(co$comment_count, decreasing = T),], n = 10)
View(top_co)
```

```{r}
rew <- ca[ca$title == "YouTube Rewind: The Shape of 2017 | #YouTubeRewind",]
sum(rew$likes) / sum(rew$likes, rew$dislikes)
sum(rew$likes) / sum(rew$views) * 100
```

Top Channel by Comment_Count
```{r}
com_count <- aggregate(comment_count~channel_title, ca, FUN = sum)
top_con <- head(com_count[order(com_count$comment_count, decreasing = T),], n = 10)
View(top_con)

connie <- ggplot(top_con, aes(channel_title, comment_count, fill = channel_title)) + 
  geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 50, hjust = 1)) +
  scale_y_continuous(labels = comma)

ggsave("chan_con.png", plot = connie, device = "png", path = "D:/Practice/Portfolio/youtube-new/Graphs", scale = 1, width = 10, height = 7)
```

Most trending date
```{r}
td <- aggregate(comment_count~trending_date, FUN = sum)
top_td <- head(td[order(td$comment_count, decreasing = T), ], n = 10)

top_date <- ca$title[ca$trending_date == "18.20.05"] 
View(top_date)
ca$comment_count[ca$trending_date == "18.20.05"]

yan <- ca[grep("Yanny",ca$title), ]

sum(yan$comment_count[yan$trending_date == "18.20.05"]) / sum(comment_count[trending_date == "18.20.05"])

vidcom <- as.data.frame(ca$title[ca$trending_date == "18.20.05"])
vidcom$comment_count <- ca$comment_count[top_date]
colnames(vidcom) <- c("Title", "Number of Comments")
vidcom <- head(vidcom[order(vidcom$`Number of Comments`, decreasing = T),], n = 10)
View(vidcom)
ca$category_id[vidcom$Title]
```


```{r}
comcat <- aggregate(comment_count~category_id, ca, FUN = sum)
names(comcat) <- c("cid", "comment_count")
colnames(items)[colnames(items)=="id"] <- "cid"

commy <- inner_join(items, comcat, by = "cid")
top_com <- commy[,c("snippet.title","comment_count")]

sum(top_com$comment_count)
(max(top_com$comment_count) - min(top_com$comment_count)) / 5

com_plot <- ggplot(top_com, aes(x = snippet.title, y = comment_count, fill = snippet.title)) + 
  geom_bar(stat = "identity") + labs(x = "Category", y = "Total Comments", fill ="Legend") + scale_y_continuous(labels = comma, breaks = seq(0,202939308, by = 11059811)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
com_plot

ggsave("top_com.png", plot = com_plot, device = "png", path = "D:/Practice/Portfolio/youtube-new/Graphs", scale = 1, width = 10, height = 7)
```



Views
```{r}
summary(views)
title[views == min(views)]
title[views == max(views)]
```

Comments
```{r}
summary(ca$comment_count)
ca$title[ca$comment_count == max(ca$comment_count)]

detach(c(ca, items))

vcom <- lm(comment_count~views+likes+dislikes, data = ca)
summary(vcom)

com_dis <- glm(comments_disabled~views+likes+dislikes, data = ca, family = "binomial")

summary(com_dis)
curve(predict(com_dis, data.frame(ca = x)))
```

Likes
```{r}
summary(ca$likes)
summary(ca$dislikes)
plot(likes~dislikes, data = ca)
plot(likes~views)

```


Top 10 Video that remained the most on the trending list
```{r}
ce <- count(title)
trendy <- head(ce[order(ce$freq, decreasing = T),], n = 10)
names(trendy) <- c("Video Title", "Trending Frequency")

View(trendy)
```


Top 10 Channels by most views
```{r}
t <- aggregate(views~channel_title,ca, FUN = sum)
top_chan <- head(t[order(t$views, decreasing = T),], n =10)

View(top_chan)

top_vi <- ggplot(data = top_chan, aes(x = channel_title, y = views, fill = channel_title)) + 
  geom_bar(stat = "identity") + labs(x = "Channel", y = "Total Views", fill = "Legend") +
  theme(axis.text.x = element_text(angle = 50, hjust = 1)) +
  scale_y_continuous(labels = comma)

ggsave("v_chan.png", plot = top_vi, device = "png", path = "D:/Practice/Portfolio/youtube-new/Graphs", scale = 1, width = 10, height = 7)
```



Number of videos per category
```{r}
category <- aggregate(video_id~category_id, ca, FUN = length)
names(category) <- c("cid", "total_videos")
category$cid <- as.character(category$cid)
#colnames(items)[colnames(items)=="id"] <- "cid"

catty <- inner_join(items, category, by = "cid")
top_cat <- catty[,c("snippet.title","total_videos")]

vcat <- ggplot(top_cat, aes(x = snippet.title, y = total_videos, fill = snippet.title)) + 
  geom_bar(stat = "identity") + labs(x = "Categories", y = "Total Videos", fill ="Legend") + 
  scale_y_continuous(labels = comma, breaks = seq(0,13451, by = 2689)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("top_vcat.png", plot = vcat, device = "png", path = "D:/Practice/Portfolio/youtube-new/Graphs", scale = 1, width = 10, height = 7)
```


# Natural Language Processing

```{r}
install.packages(c("tm", "SnowballC", "wordcloud", "e1071", "gmodels"))
install.packages("stringr")
library(stringr)
library(tm)
library(SnowballC)
library(wordcloud)
```

## tm package
Creating a Corpus (AKA a collection of documents) for the collection of tags
```{r}
tag_corpus <- VCorpus(VectorSource(ca$tags))
inspect(tag_corpus[1:2])
lapply(tag_corpus[1:4],as.character) #viewing multiple tags
```

Cleaning the text
```{r}
tag_corpus_clean <- tm_map(tag_corpus, content_transformer(tolower)) #converts to lower case
tag_corpus_clean <- tm_map(tag_corpus, removeNumbers) #remove numbers
tag_corpus_clean <- tm_map(tag_corpus, removeWords, stopwords()) #removing stop words
tag_corpus_clean <- tm_map(tag_corpus_clean, removePunctuation)
```

## SnowballC package
Stemming the Tags
```{r}
tag_corpus_clean <- tm_map(tag_corpus_clean, stemDocument)
tag_corpus_clean <- tm_map(tag_corpus_clean,stripWhitespace)
```

split messages into individual components
```{r}
tag_dtm <- DocumentTermMatrix(tag_corpus_clean)
#View(tag_dtm)
```

```{r}
install.packages("tokenizers")
library(tokenizers)

taggy1 <- gsub(pattern = "|", " ", ca$tags, fixed = T)
taggy2 <- tokenize_words(taggy1, stopwords = stopwords ::stopwords("en"))
taggy2 <- unlist(taggy2, use.names = F)
taggy2 <- plyr::count(taggy2)
taggy2 <- taggy2[grep("^(?i)[A-Z]+$",taggy2$x),]
write.csv(taggy2, file = "tagsdf.csv",row.names = F)



taggy3 <- head(taggy2[order(taggy2$freq, decreasing = T),], n = 100)
View(taggy2)
```

## Wordcloud package
Visualizing Words
```{r}
wordcloud(tag_corpus_clean,min.freq = 500,random.order = F)
```